---
title: "Climate Culture Index 2025"
subtitle: "Rare"
output:
  html_document:
    theme: flatly
    highlight: espresso
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
    toc_depth: 3
    code_folding: hide
    number_sections: false
    self_contained: true
date: '`r format(Sys.time(), "%d %B, %Y")`'
---

<style type="text/css">
/* Main container width — use div.main-container to override TOC float styles */
div.main-container {
  max-width: 1400px;
  margin-left: auto;
  margin-right: auto;
}

/* Better typography */
body {
  font-family: 'Segoe UI', Tahoma, Geneva, Verdana, sans-serif;
  line-height: 1.6;
  color: #333;
}

h1, h2, h3, h4 {
  color: #2c3e50;
  margin-top: 1.5em;
}

h1.title {
  font-size: 2.5em;
  font-weight: 700;
  color: #008542;
  border-bottom: 3px solid #008542;
  padding-bottom: 0.3em;
}

h3.subtitle {
  color: #666;
  font-weight: 400;
  margin-top: -0.5em;
}

/* Section headers */
h2 {
  border-bottom: 2px solid #e0e0e0;
  padding-bottom: 0.3em;
}

h3 {
  color: #34495e;
}

/* Collapsible details styling */
details {
  background-color: #f8f9fa;
  border: 1px solid #e9ecef;
  border-radius: 8px;
  padding: 1em;
  margin: 1em 0;
}

details summary {
  cursor: pointer;
  font-weight: 600;
  color: #2c3e50;
  padding: 0.5em;
}

details summary:hover {
  color: #008542;
}

details[open] summary {
  border-bottom: 1px solid #e9ecef;
  margin-bottom: 0.5em;
  padding-bottom: 0.5em;
}

/* Behavior cards styling */
.behavior-card {
  background: linear-gradient(135deg, #f8f9fa 0%, #ffffff 100%);
  border-radius: 10px;
  padding: 1.5em;
  margin: 1em 0;
  box-shadow: 0 2px 10px rgba(0,0,0,0.08);
  border-left: 4px solid #008542;
}

/* Table improvements */
.reactable {
  font-size: 13px;
}

/* Key findings box */
.key-finding {
  background-color: #e8f5e9;
  border-left: 4px solid #008542;
  padding: 1em 1.5em;
  margin: 1em 0;
  border-radius: 0 8px 8px 0;
}

.key-finding h4 {
  color: #008542;
  margin-top: 0;
}

/* Plot containers */
.plotly-container {
  margin: 1.5em 0;
}

/* Tab styling improvements */
.nav-tabs > li > a {
  color: #555;
  font-weight: 500;
}

.nav-tabs > li.active > a {
  color: #008542;
  border-bottom: 2px solid #008542;
}

/* Better code block styling */
pre {
  background-color: #f4f4f4;
  border-radius: 5px;
}

/* Footer */
.footer-note {
  text-align: center;
  color: #666;
  font-size: 0.9em;
  margin-top: 3em;
  padding-top: 1em;
  border-top: 1px solid #e0e0e0;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.width = 10,
  fig.height = 6,
  fig.align = 'center'
)

# Set working directory
setwd("C:/Users/RakhimRakhimov/Documents/GitHub/cci-2025-interactive")
```

```{r load-packages, include=FALSE}
# Core packages
library(haven)
library(tidyverse)
library(survey)
library(knitr)
library(magrittr)
library(readr)
library(stringr)

# Interactive visualization
library(plotly)
library(htmlwidgets)

# Tables
library(reactable)
library(DT)
library(kableExtra)

# Plotting
library(ggplot2)
library(gridExtra)
library(patchwork)
library(ggtext)
library(ggrepel)
```

```{r load-data, include=FALSE}
source("source files 2025/load-data-2025.R")
```

```{r clean-data, include=FALSE}
source("source files 2025/clean-data-2025.R")
```

```{r load-color, include=FALSE}
source("source files/table-color.R")
```

```{r sassy-segment, include=FALSE}
sassy <- read_csv("sassy_2025 Segmentation.csv")
sassy <- sassy %>% select(RID, segment)
data_2025 <- data_2025 %>% left_join(sassy, by = "RID")
```

```{r us-only, include=FALSE}
# Remove non-US specific objects and columns
rm(hist_data, lucid_2025, p, plot_data, sassy, survey_2025_full)

# Drop Boston and Denver specific columns
drop_cols <- grep("boston|denver", colnames(data_2025), value = TRUE)
data_2025 <- data_2025[, !(names(data_2025) %in% drop_cols)]
data_2025 <- data_2025 %>% select(-Vrid, -Vcomment, -Vlanguage, -Vreferer, -Vsessionid, -Vuseragent, -ResponseStatus)
```

```{r weights, include=FALSE}
source("source files 2025/national-weights.R")
rm(age_sex_race, division, education, hispanic, income, political_view, sassy, state, state_division, svy.current, svy.final, svy.rake, svy.step1, svy.step2, svy.step3, svy.step4, wt)
```

```{r data-prep, include=FALSE}
# Clean behavioral measures for 2025
data_2025 %<>% mutate(
  hp_adoption = as.numeric(hp_adoption),
  hp_adoption = case_when(hp_adoption == 1 ~ 1, TRUE ~ 0),
  community.solar_adoption = as.numeric(community.solar_adoption),
  community.solar_adoption = case_when(community.solar_adoption == 1 ~ 1, TRUE ~ 0)
) %>%
  rename(fw_adoption = fw_attempt, beef_adoption = beef_attempt)

# Create main index table
index_2025 <- data_2025 %>%
  select(
    wt, RID,
    # EVs
    ev_ne_national, ev_adoption, ev_consider, ev_ee, ev_pnb, ev_intention,
    ev_personal.benefit, ev_self.efficacy, ev_difficulty, ev_outcome.efficacy,
    ev_policy.support, ev_policy.ee, ev_policy.info, ev_policy.contact,
    # Solar
    solar_adoption, solar_ne_national, solar_pnb, solar_ee, solar_consider,
    solar_intention, solar_personal.benefit, solar_self.efficacy,
    solar_difficulty, solar_outcome.efficacy, solar_policy.support,
    solar_policy.ee, solar_policy.info, solar_policy.contact,
    # Community solar
    community.solar_adoption, community.solar_consider, community.solar_ee_national,
    community.solar_pnb, community.solar_intention, community.solar_ne_national,
    community.solar_personal.benefit, community.solar_self.efficacy,
    community.solar_difficulty, community.solar_outcome.efficacy,
    community.solar_policy.support, community.solar_policy.ee,
    community.solar_policy.info, community.solar_policy.contact,
    # Offsets
    offset_adoption, offset_consider, offset_ee_national, offset_ne_national,
    offset_intention, offset_pnb, offset_personal.benefit, offset_self.efficacy,
    offset_difficulty, offset_outcome.efficacy, offset_policy.support,
    offset_policy.ee, offset_policy.info, offset_policy.contact,
    # Heat pump
    hp_ne_national, hp_adoption, hp_consider, hp_ee_national, hp_pnb,
    hp_intention, hp_personal.benefit, hp_self.efficacy, hp_difficulty,
    hp_outcome.efficacy, hp_policy.support, hp_policy.ee, hp_policy.info,
    hp_policy.contact,
    # Beef
    beef_adoption, beef_consider, beef_difficulty, beef_ee_national, beef_pnb,
    beef_ne_national, beef_intention, beef_personal.benefit, beef_self.efficacy,
    beef_outcome.efficacy, beef_policy.support, beef_policy.ee, beef_policy.info,
    beef_policy.contact,
    # Food waste
    fw_adoption, fw_consider, fw_pnb, fw_ee_national, fw_ne_national,
    fw_intention, fw_personal.benefit, fw_self.efficacy, fw_difficulty,
    fw_outcome.efficacy, fw_policy.support, fw_policy.ee, fw_policy.info,
    fw_policy.contact,
    # Demographics
    age_group, sex, race, HISPANIC, political_viewpoint_wvs, political_party, income
  )

# Clean behavioral variables
index_2025 %<>% mutate(
  ev_adoption = case_when(ev_adoption %in% 1:5 ~ 1, TRUE ~ 0),
  ev_policy.support = case_when(ev_policy.support %in% c(3, 4) ~ 1, ev_policy.support %in% c(1, 2) ~ 0),
  solar_policy.support = case_when(solar_policy.support %in% c(3, 4) ~ 1, solar_policy.support %in% c(1, 2) ~ 0),
  community.solar_policy.support = case_when(community.solar_policy.support %in% c(3, 4) ~ 1, community.solar_policy.support %in% c(1, 2) ~ 0),
  offset_policy.support = case_when(offset_policy.support %in% c(3, 4) ~ 1, offset_policy.support %in% c(1, 2) ~ 0),
  hp_policy.support = case_when(hp_policy.support %in% c(3, 4) ~ 1, hp_policy.support %in% c(1, 2) ~ 0),
  beef_policy.support = case_when(beef_policy.support %in% c(3, 4) ~ 1, beef_policy.support %in% c(1, 2) ~ 0),
  fw_policy.support = case_when(fw_policy.support %in% c(3, 4) ~ 1, fw_policy.support %in% c(1, 2) ~ 0)
)

# Save demographics version for later analysis
survey_2025_with_demos <- index_2025

# Create clean survey dataset
index_2025 <- index_2025 %>% select(RID, wt, ev_ne_national:fw_policy.contact)
survey_2025 <- index_2025
index_2025 <- mutate_all(index_2025, function(x) as.numeric(as.character(x)))
```

```{r table-prep, include=FALSE}
# Pivot to long format
index_long <- index_2025 %>%
  pivot_longer(
    cols = contains(c("intention", "ee", "pnb", "ne", "adoption", "consider",
                      "personal.benefit", "self.efficacy", "outcome.efficacy",
                      "difficulty", "policy.support", "policy.ee", "policy.info",
                      "policy.contact")),
    names_to = "indicator",
    values_to = "value",
    values_drop_na = TRUE
  )

index_long <- index_long %>% mutate(behavior = indicator)
fin_table <- index_long %>%
  mutate(behavior = sapply(strsplit(indicator, split = '_', fixed = TRUE), function(x) x[1]))

fin_table <- fin_table %>%
  mutate(ind = sapply(strsplit(indicator, split = '_', fixed = TRUE), function(x) x[2]))

fin_table %<>% select(-RID, -indicator)

t1 <- group_by(fin_table, behavior, ind)
t1 <- summarise(t1, w.mean = weighted.mean(value, wt, na.rm = TRUE))
t1 %<>% group_by(behavior) %>% pivot_wider(names_from = ind, values_from = w.mean)

# Format values
t1 <- t1 %>%
  mutate(
    adoption = adoption * 100,
    consider = consider * 100,
    ee = ee * 10,
    ne = ne * 10,
    pnb = pnb * 100,
    personal.benefit = (personal.benefit - 1) / 4 * 100,
    outcome.efficacy = (outcome.efficacy - 1) / 4 * 100,
    self.efficacy = (self.efficacy - 1) / 4 * 100,
    policy.contact = policy.contact * 100,
    policy.info = policy.info * 100,
    policy.support = policy.support * 100,
    policy.ee = policy.ee * 10
  )

# Rename columns
t1 <- t1 %>%
  rename(
    'Behavior' = behavior,
    'Consideration' = consider,
    'Adoption' = adoption,
    'Intention' = intention,
    'Belief that others are engaging in the behavior' = ee,
    'Belief that others should engage in the behavior' = pnb,
    'Belief that others think people should engage in the behavior' = ne,
    'Self-efficacy' = self.efficacy,
    'Outcome efficacy' = outcome.efficacy,
    'Perceived personal benefit' = personal.benefit,
    'Perceived ease of adoption' = difficulty,
    'Policy support' = policy.support,
    'Perceived policy support' = policy.ee,
    'Openness to learn about the policy' = policy.info,
    'Openness to contact a representative' = policy.contact
  )

# Rename behavior labels
t1$Behavior[t1$Behavior == "ev"] <- "Drive an EV"
t1$Behavior[t1$Behavior == "offset"] <- "Buy carbon offsets"
t1$Behavior[t1$Behavior == "solar"] <- "Install solar panels"
t1$Behavior[t1$Behavior == "beef"] <- "Eat less beef"
t1$Behavior[t1$Behavior == "community.solar"] <- "Sign up for community solar"
t1$Behavior[t1$Behavior == "fw"] <- "Reduce food waste"
t1$Behavior[t1$Behavior == "hp"] <- "Install a heat pump"

# Reorder columns
t1 <- t1 %>% select(
  Behavior, Consideration, Adoption, Intention,
  `Belief that others are engaging in the behavior`,
  `Belief that others should engage in the behavior`,
  `Belief that others think people should engage in the behavior`,
  `Self-efficacy`, `Outcome efficacy`,
  `Perceived personal benefit`, `Perceived ease of adoption`,
  `Policy support`, `Perceived policy support`,
  `Openness to learn about the policy`, `Openness to contact a representative`
)
```

```{r define-colors, include=FALSE}
# Define consistent behavior colors used throughout
behavior_colors <- c(
  "Drive an EV" = "#005BBB",
  "Buy carbon offsets" = "#5E6A71",
  "Install solar panels" = "#F58233",
  "Sign up for community solar" = "#008542",
  "Install a heat pump" = "#7f5d90",
  "Eat less beef" = "#AA1948",
  "Reduce food waste" = "#884600"
)

# Behaviors mapping
behaviors <- c(
  "ev" = "Drive an EV",
  "solar" = "Install solar panels",
  "community.solar" = "Sign up for community solar",
  "offset" = "Buy carbon offsets",
  "hp" = "Install a heat pump",
  "beef" = "Eat less beef",
  "fw" = "Reduce food waste"
)
```

## Overview {.tabset}

### Background

Understanding the public's opinions and beliefs towards climate change and climate action can inform the development of behavior-change campaigns and support tailored communication strategies. However, previous studies have mostly focused on examining trends in [climate policy support](https://climatecommunication.yale.edu/visualizations-data/americans-climate-views/), [risk perceptions](https://www.pewresearch.org/short-reads/2023/04/18/for-earth-day-key-facts-about-americans-views-of-climate-change-and-renewable-energy/), or [broad beliefs around climate change](https://news.gallup.com/poll/355427/americans-concerned-global-warming.aspx).

The **Climate Culture Index (CCI)** fills this gap by tracking key indicators that were found to support behavior change for a set of high-impact climate-mitigating behaviors. The CCI is designed to measure changes in these indicators over time, helping us understand potential shifts in the American public's beliefs around climate behaviors.

**Prior Studies:**

- [Climate Culture Index, 2021](https://rakhimovr.github.io/cc-index-2021/index_external.html)
- [Climate Culture IRA Index, 2023](https://climateculture.github.io/cc-ira-index-2023/cc-ira-index-2023.html)
- [Climate Culture Index, 2023](https://climateculture.github.io/cc-index-2023/cc-index-2023.html)
- [Climate Culture Index, 2024](https://rakhimovr.github.io/cci-24/cci-24.html)

### Seven Climate Behaviors

In this study, we measured beliefs and psycho-social states for the following seven high-impact behaviors:

1. Eat less beef
2. Reduce food waste
3. Buy an Electric Vehicle (EV)
4. Install solar panels
5. Sign up for community solar
6. Buy carbon offsets
7. Install a heat pump

The survey instrument is available [here](https://drive.google.com/file/d/13LRS4yGWrfPR4FUPrjyWwVI38b0WCVvu/view?usp=sharing).

### Methodology

In **August 2025**, we surveyed adults online from the United States (n = 1,828), quota-matched on demographic variables including age group, gender, and ethnicity.

For the analyses, the national sample was weighted using survey weights to be representative of the US adult population in:

- Age group x gender x ethnicity
- Hispanic/non-Hispanic origin
- Highest level of education completed
- Annual household income before taxes
- State population
- Political viewpoint
- Segments of Global Warming's Six Americas

---

## Climate Culture Index {.tabset}

### Main Index Table

The table below shows the weighted means for each psychosocial indicator across all seven behaviors. **Click on column headers to sort**.

```{r main-table}
reactable(
  t1,
  style = list(fontSize = "12px"),
  defaultSortOrder = 'asc',
  defaultSorted = 'Behavior',
  showSortIcon = TRUE,
  pagination = TRUE,
  compact = TRUE,
  borderless = FALSE,
  striped = TRUE,
  highlight = TRUE,
  fullWidth = TRUE,
  defaultColDef = colDef(minWidth = 60, align = "center", format = colFormat(digits = 1)),
  theme = reactableTheme(
    headerStyle = list(
      "&:hover[aria-sort]" = list(background = "hsl(0, 0%, 96%)"),
      "&[aria-sort='ascending'], &[aria-sort='descending']" = list(background = "hsl(0, 0%, 96%)"),
      borderColor = "#555"
    )
  ),
  columns = list(
    Behavior = colDef(
      align = "left",
      minWidth = 140,
      sticky = "left",
      style = list(borderLeft = "1px solid #eee", fontWeight = "bold"),
      headerStyle = list(borderLeft = "1px solid #eee")
    ),
    Adoption = colDef(
      name = "Reported adoption (%)",
      style = function(value) {
        normalized <- (value - min(t1$Adoption)) / (max(t1$Adoption) - min(t1$Adoption))
        color <- good_color(normalized)
        list(background = color)
      }
    ),
    Intention = colDef(
      name = "Avg intention (0-100)",
      style = function(value) {
        normalized <- (value - min(t1$Intention)) / (max(t1$Intention) - min(t1$Intention))
        color <- good_color(normalized)
        list(background = color)
      }
    ),
    `Belief that others are engaging in the behavior` = colDef(
      name = "Others adopted (%)",
      style = function(value) {
        normalized <- (value - min(t1$`Belief that others are engaging in the behavior`)) /
                      (max(t1$`Belief that others are engaging in the behavior`) - min(t1$`Belief that others are engaging in the behavior`))
        color <- good_color(normalized)
        list(background = color)
      }
    ),
    `Belief that others should engage in the behavior` = colDef(
      name = "Others should adopt (%)",
      style = function(value) {
        normalized <- (value - min(t1$`Belief that others should engage in the behavior`)) /
                      (max(t1$`Belief that others should engage in the behavior`) - min(t1$`Belief that others should engage in the behavior`))
        color <- good_color(normalized)
        list(background = color)
      }
    ),
    `Belief that others think people should engage in the behavior` = colDef(
      name = "Others think people should (%)",
      style = function(value) {
        normalized <- (value - min(t1$`Belief that others think people should engage in the behavior`)) /
                      (max(t1$`Belief that others think people should engage in the behavior`) - min(t1$`Belief that others think people should engage in the behavior`))
        color <- good_color(normalized)
        list(background = color)
      }
    ),
    `Self-efficacy` = colDef(
      style = function(value) {
        normalized <- (value - min(t1$`Self-efficacy`)) / (max(t1$`Self-efficacy`) - min(t1$`Self-efficacy`))
        color <- good_color(normalized)
        list(background = color)
      }
    ),
    Consideration = colDef(
      name = "Consideration (%)",
      style = function(value) {
        normalized <- (value - min(t1$Consideration)) / (max(t1$Consideration) - min(t1$Consideration))
        color <- good_color(normalized)
        list(background = color)
      }
    ),
    `Perceived personal benefit` = colDef(
      name = "Personal benefit",
      style = function(value) {
        normalized <- (value - min(t1$`Perceived personal benefit`)) /
                      (max(t1$`Perceived personal benefit`) - min(t1$`Perceived personal benefit`))
        color <- good_color(normalized)
        list(background = color)
      }
    ),
    `Outcome efficacy` = colDef(
      style = function(value) {
        normalized <- (value - min(t1$`Outcome efficacy`)) / (max(t1$`Outcome efficacy`) - min(t1$`Outcome efficacy`))
        color <- good_color(normalized)
        list(background = color)
      }
    ),
    `Perceived ease of adoption` = colDef(
      name = "Difficulty (0-100)",
      style = function(value) {
        normalized <- (value - min(t1$`Perceived ease of adoption`)) /
                      (max(t1$`Perceived ease of adoption`) - min(t1$`Perceived ease of adoption`))
        color <- good_color(normalized)
        list(background = color)
      }
    ),
    `Policy support` = colDef(
      name = "Policy support (%)",
      style = function(value) {
        normalized <- (value - min(t1$`Policy support`)) / (max(t1$`Policy support`) - min(t1$`Policy support`))
        color <- good_color(normalized)
        list(background = color)
      }
    ),
    `Perceived policy support` = colDef(
      name = "Perceived support (%)",
      style = function(value) {
        normalized <- (value - min(t1$`Perceived policy support`)) /
                      (max(t1$`Perceived policy support`) - min(t1$`Perceived policy support`))
        color <- good_color(normalized)
        list(background = color)
      }
    ),
    `Openness to learn about the policy` = colDef(
      name = "Learn about policy (%)",
      style = function(value) {
        normalized <- (value - min(t1$`Openness to learn about the policy`)) /
                      (max(t1$`Openness to learn about the policy`) - min(t1$`Openness to learn about the policy`))
        color <- good_color(normalized)
        list(background = color)
      }
    ),
    `Openness to contact a representative` = colDef(
      name = "Contact rep (%)",
      style = function(value) {
        normalized <- (value - min(t1$`Openness to contact a representative`)) /
                      (max(t1$`Openness to contact a representative`) - min(t1$`Openness to contact a representative`))
        color <- good_color(normalized)
        list(background = color)
      }
    )
  ),
  columnGroups = list(
    colGroup(name = "Beliefs that...", columns = c(
      "Belief that others are engaging in the behavior",
      "Belief that others should engage in the behavior",
      "Belief that others think people should engage in the behavior"
    )),
    colGroup(name = "Openness to...", columns = c(
      "Openness to learn about the policy",
      "Openness to contact a representative"
    ))
  )
)
```

### Behavioral Measures

<details>
<summary><strong>Click to expand: Detailed measure descriptions</strong></summary>

For the seven climate behaviors, we measured ten indicators identified as either important enablers or predictors of climate action:

| Indicator | Description | Example Question |
|-----------|-------------|------------------|
| **Consideration** | Whether the person has considered adopting the behavior | *Before taking this survey, have you ever considered getting a fully electric car?* |
| **Reported adoption** | Reported adoption of the behavior | *Does your household have solar panels installed?* |
| **Reported intention** | Intention to perform the behavior in the near future | *How likely is it that you will limit your beef consumption in the next 12 months?* |
| **Belief that others have adopted** | Perceived number of others that have adopted (empirical expectations) | *Imagine 10 households you know. How many do you think get their electricity from community solar?* |
| **Belief that others should adopt** | Personal normative beliefs about adoption | *Do you think people should purchase carbon offsets because it is the right thing to do?* |
| **Beliefs that others think people should adopt** | Normative expectations | *Imagine 10 people you know. How many think people should use an electric heat pump?* |
| **Self-efficacy** | Belief in one's ability to adopt | *How confident are you in your ability to purchase and drive a fully electric car?* |
| **Outcome efficacy** | Belief that adoption carries climate benefits | *How confident are you that driving an EV will reduce your carbon emissions?* |
| **Personal benefit** | Stated personal benefit from adoption | *How much do you think limiting beef consumption would benefit you personally?* |
| **Perceived ease of adoption** | Reported ease of adopting | *How difficult would it be for you to get electricity from community solar?* |

</details>

### Climate Policies

For each behavior, we included 4 policy-related measures: **policy support, perceived policy support, openness to learn about the policy, and openness to contact a representative**.

```{r policy-table}
policy_table <- data.frame(
  Behavior = c(
    "Drive an EV",
    "Install solar panels",
    "Sign up for community solar",
    "Buy carbon offsets",
    "Install a heat pump",
    "Eat less beef",
    "Reduce food waste"
  ),
  `Policy Description` = c(
    "Your state provides an upfront cash rebate for the purchase or lease of a fully electric vehicle",
    "When solar panels produce more electricity than a home consumes, your utility offers to buy that excess electricity, lowering the homeowner's utility bill",
    "Your utility guarantees households who sign up for community solar energy at least 5% savings on their annual electricity cost",
    "The federal government requires all travel providers to offer customers an option to purchase carbon offsets",
    "Your state provides an upfront cash rebate for the purchase of a heat pump",
    "Your state increases the availability of vegetable and plant-based options in state-owned facilities",
    "The federal government establishes a uniform food date labeling system to help consumers make accurate decisions about discarding food"
  ),
  check.names = FALSE
)

policy_table$Behavior <- paste0(
  "<span style='color:", behavior_colors[policy_table$Behavior], "; font-weight: bold;'>",
  policy_table$Behavior,
  "</span>"
)

kable(policy_table,
      caption = "Climate Policy Descriptions by Behavior",
      format = "html",
      escape = FALSE,
      align = c("l", "l")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = TRUE,
                position = "left") %>%
  column_spec(1, width = "25%") %>%
  column_spec(2, width = "75%")
```

---

## Trends in Psychosocial Indicators {.tabset}

```{r trends-data-prep, include=FALSE}
# Load historical data
trends_2024 <- read.csv("trends_2024.csv")

# Rename _national columns to match
survey_2025_processed <- survey_2025
national_cols <- grep("_national$", colnames(survey_2025_processed), value = TRUE)
base_names <- gsub("_national$", "", national_cols)

for (i in seq_along(national_cols)) {
  old_name <- national_cols[i]
  new_name <- base_names[i]
  if (new_name %in% colnames(trends_2024)) {
    colnames(survey_2025_processed)[colnames(survey_2025_processed) == old_name] <- new_name
  }
}

# Get matching columns
matching_cols <- intersect(colnames(trends_2024), colnames(survey_2025_processed))
survey_2025_subset <- survey_2025_processed[, matching_cols, drop = FALSE]
survey_2025_subset$wave <- 2025

if (!"wave" %in% colnames(trends_2024)) {
  trends_2024$wave <- 2024
}

# Combine datasets
combined_df <- rbind(trends_2024, survey_2025_subset[, colnames(trends_2024)])
combined_df <- mutate_all(combined_df, function(x) as.numeric(as.character(x)))

# Prepare summary data
behavior_mapping <- c(
  "ev" = "Drive an EV", "solar" = "Install solar panels", "offset" = "Buy carbon offsets",
  "community.solar" = "Sign up for community solar", "hp" = "Install a heat pump",
  "beef" = "Eat less beef", "fw" = "Reduce food waste"
)

name_mapping <- c(
  "adoption" = "Reported adoption", "consider" = "Consideration", "intention" = "Reported intention",
  "ee" = "Empirical expectations", "pnb" = "Personal normative beliefs",
  "ne" = "Normative expectations", "self.efficacy" = "Self-efficacy",
  "personal.benefit" = "Personal benefit", "outcome.efficacy" = "Outcome efficacy",
  "difficulty" = "Perceived difficulty",
  "policy.support" = "Policy support", "policy.ee" = "Perceived policy support",
  "policy.info" = "Openness to learn about policy", "policy.contact" = "Willingness to contact representative"
)

# Long format with labels
long <- combined_df %>%
  pivot_longer(cols = -c(RID, wave, wt),
               names_to = c("behavior", "measure"),
               names_pattern = "^(.+?)_(.+)$",
               values_to = "value") %>%
  mutate(
    behavior_label = behavior_mapping[behavior],
    measure_label = name_mapping[measure]
  )

df_summary <- long %>%
  filter(!is.na(value)) %>%
  group_by(wave, behavior, measure, behavior_label, measure_label) %>%
  summarise(
    n = n(),
    mean = weighted.mean(value, w = wt, na.rm = TRUE),
    weighted_var = sum(wt * (value - weighted.mean(value, w = wt, na.rm = TRUE))^2) / sum(wt),
    weighted_sd = sqrt(weighted_var),
    se = weighted_sd / sqrt(n()),
    conf.low = mean - qt(0.975, df = n() - 1) * se,
    conf.high = mean + qt(0.975, df = n() - 1) * se,
    .groups = "drop"
  )

# Rescale measures
df_summary <- df_summary %>%
  mutate(
    mean = ifelse(measure_label %in% c("Reported adoption", "Consideration", "Personal normative beliefs"),
                  mean * 100, mean),
    conf.low = ifelse(measure_label %in% c("Reported adoption", "Consideration", "Personal normative beliefs"),
                      conf.low * 100, conf.low),
    conf.high = ifelse(measure_label %in% c("Reported adoption", "Consideration", "Personal normative beliefs"),
                       conf.high * 100, conf.high),
    mean = ifelse(measure_label %in% c("Empirical expectations", "Normative expectations"), mean * 10, mean),
    conf.low = ifelse(measure_label %in% c("Empirical expectations", "Normative expectations"), conf.low * 10, conf.low),
    conf.high = ifelse(measure_label %in% c("Empirical expectations", "Normative expectations"), conf.high * 10, conf.high)
  )

measures_to_scale <- c("Self-efficacy", "Outcome efficacy", "Personal benefit")
df_summary <- df_summary %>%
  mutate(across(c(mean, conf.low, conf.high),
                ~ if_else(measure_label %in% measures_to_scale, (. - 1) / 4 * 100, .)))
```

```{r create-interactive-plot-function, include=FALSE}
# Function to create interactive plotly trend plots
create_trend_plot <- function(data, measure_name, y_label = "%", title_suffix = "") {

  plot_data <- data %>% filter(measure_label == measure_name)

  if (nrow(plot_data) == 0) return(NULL)

  # Create legend order based on 2025 values
  legend_order <- plot_data %>%
    filter(wave == 2025) %>%
    arrange(desc(mean)) %>%
    pull(behavior_label)

  plot_data$behavior_label <- factor(plot_data$behavior_label, levels = legend_order)

  p <- ggplot(plot_data, aes(x = factor(wave), y = mean,
                              group = behavior_label, color = behavior_label)) +
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high),
                  width = 0.15, alpha = 0.5, position = position_dodge(width = 0.1)) +
    geom_line(position = position_dodge(width = 0.1), linewidth = 0.8) +
    geom_point(size = 2.5, position = position_dodge(width = 0.1), alpha = 0.8) +
    scale_color_manual(values = behavior_colors) +
    scale_x_discrete(labels = c("2024", "2025")) +
    labs(
      title = paste0(measure_name, title_suffix),
      subtitle = paste0("% of U.S. adults, weighted estimates with 95% CIs"),
      x = "", y = y_label, color = "Behavior",
      caption = "Source: Climate Culture Index, Rare, 2025"
    ) +
    theme_minimal() +
    theme(
      text = element_text(family = "sans"),
      legend.position = "bottom",
      legend.title = element_blank(),
      plot.title = element_text(size = 12, face = "bold"),
      plot.subtitle = element_text(size = 9, color = "grey50"),
      axis.text = element_text(size = 9),
      panel.grid.minor = element_blank()
    ) +
    guides(color = guide_legend(nrow = 2))

  # Convert to plotly
  ggplotly(p, tooltip = c("x", "y", "color")) %>%
    layout(
      legend = list(orientation = "h", y = -0.2),
      margin = list(b = 100)
    )
}
```

### Consideration

```{r plot-consideration}
create_trend_plot(df_summary, "Consideration", y_label = "% who have considered")
```

### Reported Adoption

```{r plot-adoption}
create_trend_plot(df_summary, "Reported adoption", y_label = "% who have adopted")
```

### Reported Intention

```{r plot-intention}
create_trend_plot(df_summary, "Reported intention", y_label = "Average intention (0-100)")
```

### Empirical Expectations

```{r plot-ee}
create_trend_plot(df_summary, "Empirical expectations", y_label = "Perceived % of others who adopted")
```

### Personal Normative Beliefs

```{r plot-pnb}
create_trend_plot(df_summary, "Personal normative beliefs", y_label = "% who believe others should adopt")
```

### Normative Expectations

```{r plot-ne}
create_trend_plot(df_summary, "Normative expectations", y_label = "Perceived % who think people should adopt")
```

### Self-efficacy

```{r plot-se}
create_trend_plot(df_summary, "Self-efficacy", y_label = "Confidence in ability (0-100)")
```

### Personal Benefit

```{r plot-pb}
create_trend_plot(df_summary, "Personal benefit", y_label = "Perceived benefit (0-100)")
```

---

## Trends in Policy Measures {.tabset}

```{r policy-data-prep, include=FALSE}
# Load 2024 data for policy analysis
survey_2024 <- read_sav("data/2024/survey_2024.sav")

# Helper function for consistent numeric conversion
to_numeric_consistent <- function(df, cols) {
  df %>%
    mutate(across(all_of(cols), \(x) {
      if (inherits(x, "haven_labelled")) {
        as.numeric(haven::zap_labels(x))
      } else if (is.numeric(x)) {
        as.numeric(x)
      } else if (is.character(x)) {
        suppressWarnings(readr::parse_number(x))
      } else if (is.factor(x)) {
        lev <- levels(x)
        nums <- suppressWarnings(as.numeric(lev))
        if (!any(is.na(nums))) as.numeric(as.character(x)) else as.integer(x)
      } else {
        suppressWarnings(as.numeric(x))
      }
    }))
}

difficulty_cols <- c("ev_difficulty", "solar_difficulty", "community.solar_difficulty",
                     "offset_difficulty", "hp_difficulty", "beef_difficulty", "fw_difficulty")

survey_2024_fix <- survey_2024 %>% to_numeric_consistent(difficulty_cols) %>% mutate(wave = 2024)
survey_2025_fix <- survey_2025 %>% to_numeric_consistent(difficulty_cols) %>% mutate(wave = 2025)

common <- intersect(names(survey_2024_fix), names(survey_2025_fix))
survey_24_25 <- rbind(survey_2024_fix[common], survey_2025_fix[common])
```

### Policy Support

```{r policy-support-plot}
policy_support_estimates <- survey_24_25 %>%
  select(wave, wt, ends_with("_policy.support")) %>%
  pivot_longer(cols = ends_with("_policy.support"), names_to = "behavior_var", values_to = "policy_support") %>%
  mutate(behavior_var = str_remove(behavior_var, "_policy\\.support"),
         behavior_label = unname(behaviors[behavior_var])) %>%
  filter(!is.na(policy_support), !is.na(wt), !is.na(behavior_label)) %>%
  group_by(behavior_label, wave) %>%
  summarise(
    mean = weighted.mean(policy_support, wt, na.rm = TRUE) * 100,
    n = n(),
    se = sqrt((mean/100) * (1 - mean/100) / n) * 100,
    conf.low = pmax(0, mean - 1.96 * se),
    conf.high = pmin(100, mean + 1.96 * se),
    .groups = "drop"
  )

legend_order <- policy_support_estimates %>% filter(wave == 2025) %>% arrange(desc(mean)) %>% pull(behavior_label)
policy_support_estimates$behavior_label <- factor(policy_support_estimates$behavior_label, levels = legend_order)

p <- ggplot(policy_support_estimates, aes(x = factor(wave), y = mean, group = behavior_label, color = behavior_label)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.15, alpha = 0.5) +
  geom_line(linewidth = 0.8) +
  geom_point(size = 2.5) +
  scale_color_manual(values = behavior_colors) +
  scale_y_continuous(labels = function(x) paste0(x, "%"), limits = c(55, 95)) +
  labs(title = "U.S. adult support for climate policies",
       subtitle = "% of U.S. adults who say they support policies to promote climate actions",
       x = "", y = "", color = "",
       caption = "Source: Climate Culture Index, Rare, 2025") +
  theme_minimal() +
  theme(legend.position = "bottom", plot.title = element_text(face = "bold")) +
  guides(color = guide_legend(nrow = 2))

ggplotly(p, tooltip = c("x", "y", "color")) %>% layout(legend = list(orientation = "h", y = -0.2))
```

### Openness to Learn About Policy

```{r policy-info-plot}
policy_info_estimates <- survey_24_25 %>%
  select(wave, wt, ends_with("_policy.info")) %>%
  pivot_longer(cols = ends_with("_policy.info"), names_to = "behavior_var", values_to = "policy_info") %>%
  mutate(behavior_var = str_remove(behavior_var, "_policy\\.info"),
         behavior_label = unname(behaviors[behavior_var])) %>%
  filter(!is.na(policy_info), !is.na(wt), !is.na(behavior_label)) %>%
  group_by(behavior_label, wave) %>%
  summarise(
    mean = weighted.mean(policy_info, wt, na.rm = TRUE) * 100,
    n = n(),
    se = sqrt((mean/100) * (1 - mean/100) / n) * 100,
    conf.low = pmax(0, mean - 1.96 * se),
    conf.high = pmin(100, mean + 1.96 * se),
    .groups = "drop"
  )

legend_order <- policy_info_estimates %>% filter(wave == 2025) %>% arrange(desc(mean)) %>% pull(behavior_label)
policy_info_estimates$behavior_label <- factor(policy_info_estimates$behavior_label, levels = legend_order)

p <- ggplot(policy_info_estimates, aes(x = factor(wave), y = mean, group = behavior_label, color = behavior_label)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.15, alpha = 0.5) +
  geom_line(linewidth = 0.8) +
  geom_point(size = 2.5) +
  scale_color_manual(values = behavior_colors) +
  scale_y_continuous(labels = function(x) paste0(x, "%"), limits = c(10, 30)) +
  labs(title = "U.S. adult openness to learn about climate policies",
       subtitle = "% of U.S. adults interested in learning about policies to promote climate actions",
       x = "", y = "", color = "",
       caption = "Source: Climate Culture Index, Rare, 2025") +
  theme_minimal() +
  theme(legend.position = "bottom", plot.title = element_text(face = "bold")) +
  guides(color = guide_legend(nrow = 2))

ggplotly(p, tooltip = c("x", "y", "color")) %>% layout(legend = list(orientation = "h", y = -0.2))
```

### Willingness to Contact Representative

```{r policy-contact-plot}
policy_contact_estimates <- survey_24_25 %>%
  select(wave, wt, ends_with("_policy.contact")) %>%
  pivot_longer(cols = ends_with("_policy.contact"), names_to = "behavior_var", values_to = "policy_contact") %>%
  mutate(behavior_var = str_remove(behavior_var, "_policy\\.contact"),
         behavior_label = unname(behaviors[behavior_var])) %>%
  filter(!is.na(policy_contact), !is.na(wt), !is.na(behavior_label)) %>%
  group_by(behavior_label, wave) %>%
  summarise(
    mean = weighted.mean(policy_contact, wt, na.rm = TRUE) * 100,
    n = n(),
    se = sqrt((mean/100) * (1 - mean/100) / n) * 100,
    conf.low = pmax(0, mean - 1.96 * se),
    conf.high = pmin(100, mean + 1.96 * se),
    .groups = "drop"
  )

legend_order <- policy_contact_estimates %>% filter(wave == 2025) %>% arrange(desc(mean)) %>% pull(behavior_label)
policy_contact_estimates$behavior_label <- factor(policy_contact_estimates$behavior_label, levels = legend_order)

p <- ggplot(policy_contact_estimates, aes(x = factor(wave), y = mean, group = behavior_label, color = behavior_label)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.15, alpha = 0.5) +
  geom_line(linewidth = 0.8) +
  geom_point(size = 2.5) +
  scale_color_manual(values = behavior_colors) +
  scale_y_continuous(labels = function(x) paste0(x, "%"), limits = c(5, 22)) +
  labs(title = "U.S. adult willingness to contact representatives",
       subtitle = "% willing to contact representatives to express support for climate policies",
       x = "", y = "", color = "",
       caption = "Source: Climate Culture Index, Rare, 2025") +
  theme_minimal() +
  theme(legend.position = "bottom", plot.title = element_text(face = "bold")) +
  guides(color = guide_legend(nrow = 2))

ggplotly(p, tooltip = c("x", "y", "color")) %>% layout(legend = list(orientation = "h", y = -0.2))
```

### Perceived Policy Support

```{r policy-ee-plot}
policy_ee_estimates <- survey_24_25 %>%
  select(wave, wt, ends_with("_policy.ee")) %>%
  pivot_longer(cols = ends_with("_policy.ee"), names_to = "behavior_var", values_to = "policy_ee") %>%
  mutate(behavior_var = str_remove(behavior_var, "_policy\\.ee"),
         behavior_label = unname(behaviors[behavior_var])) %>%
  filter(!is.na(policy_ee), !is.na(wt), !is.na(behavior_label)) %>%
  group_by(behavior_label, wave) %>%
  summarise(
    mean = weighted.mean(policy_ee, wt, na.rm = TRUE) * 10,
    n = n(),
    se = sqrt((mean/100) * (1 - mean/100) / n) * 100,
    conf.low = pmax(0, mean - 1.96 * se),
    conf.high = pmin(100, mean + 1.96 * se),
    .groups = "drop"
  )

legend_order <- policy_ee_estimates %>% filter(wave == 2025) %>% arrange(desc(mean)) %>% pull(behavior_label)
policy_ee_estimates$behavior_label <- factor(policy_ee_estimates$behavior_label, levels = legend_order)

p <- ggplot(policy_ee_estimates, aes(x = factor(wave), y = mean, group = behavior_label, color = behavior_label)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.15, alpha = 0.5) +
  geom_line(linewidth = 0.8) +
  geom_point(size = 2.5) +
  scale_color_manual(values = behavior_colors) +
  scale_y_continuous(labels = function(x) paste0(x, "%"), limits = c(25, 65)) +
  labs(title = "U.S. adult perceptions of policy support",
       subtitle = "% of U.S. adults believed to support policies to promote climate actions",
       x = "", y = "", color = "",
       caption = "Source: Climate Culture Index, Rare, 2025") +
  theme_minimal() +
  theme(legend.position = "bottom", plot.title = element_text(face = "bold")) +
  guides(color = guide_legend(nrow = 2))

ggplotly(p, tooltip = c("x", "y", "color")) %>% layout(legend = list(orientation = "h", y = -0.2))
```

---

## Policy Support Gap

The following chart shows the gap between **perceived policy support** (what people think others believe) and **actual policy support** (what people actually believe).

```{r policy-gap-plot, fig.height=7}
# Prepare data for policy support gap
gap_data <- t1 %>%
  select(Behavior, `Policy support`, `Perceived policy support`) %>%
  mutate(gap = `Policy support` - `Perceived policy support`)

p <- ggplot(gap_data) +
  geom_segment(aes(x = reorder(Behavior, `Policy support`), xend = Behavior,
                   y = `Perceived policy support`, yend = `Policy support`),
               color = "grey70", linewidth = 3, alpha = 0.6) +
  geom_point(aes(x = Behavior, y = `Perceived policy support`,
                 color = "Perceived % supporting"), size = 5) +
  geom_point(aes(x = Behavior, y = `Policy support`,
                 color = "Actual % supporting"), size = 5) +
  coord_flip() +
  scale_color_manual(values = c("Actual % supporting" = "#008542",
                                "Perceived % supporting" = "#F58233")) +
  scale_y_continuous(labels = function(x) paste0(x, "%"), limits = c(0, 100)) +
  labs(
    title = "Climate Policy Support Gap",
    subtitle = "Comparison of actual vs. perceived policy support among U.S. adults",
    x = "", y = "% of U.S. adults",
    color = "",
    caption = "Source: Climate Culture Index, Rare, 2025"
  ) +
  theme_minimal() +
  theme(
    legend.position = "top",
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 11, color = "grey50"),
    axis.text.y = element_text(size = 11),
    panel.grid.major.y = element_blank()
  )

ggplotly(p, tooltip = c("y", "color")) %>%
  layout(legend = list(orientation = "h", y = 1.1))
```

---

## Political Party Analysis {.tabset}

This section examines how policy support and willingness to contact representatives varies by political party affiliation.

```{r party-data-prep, include=FALSE}
# Load 2024 SPSS data to get political party information
spss_2024 <- read_sav("data/2024/spss_2024.sav")

# Extract party info from 2024
party_viewpoint_2024 <- spss_2024 %>%
  select(RID, political_party, political_viewpoint_wvs)

# Clean and merge 2024 data
survey_2024_clean <- survey_2024_fix %>%
  select(-any_of(c("political_party", "political_viewpoint_wvs")))
survey_2024_with_party <- survey_2024_clean %>%
  left_join(party_viewpoint_2024, by = "RID")

# Extract party info from 2025
party_viewpoint_2025 <- survey_2025_with_demos %>%
  select(RID, political_party, political_viewpoint_wvs)

survey_2025_clean <- survey_2025_fix %>%
  select(-any_of(c("political_party", "political_viewpoint_wvs")))
survey_2025_with_party <- survey_2025_clean %>%
  left_join(party_viewpoint_2025, by = "RID")

# Combine both years
common_cols <- intersect(names(survey_2024_with_party), names(survey_2025_with_party))
survey_24_25_with_party <- rbind(
  survey_2024_with_party %>% select(all_of(common_cols)),
  survey_2025_with_party %>% select(all_of(common_cols))
)

# Define party colors
party_colors <- c(
  "Democrats" = "#0044c9",
  "Republicans" = "#da1333",
  "Independent/Other" = "#F18F01",
  "No Party Affiliation" = "grey50"
)

# Helper function for binary conversion
to01 <- function(x, treat_1to4_as_binary = FALSE) {
  if (is.factor(x)) x <- as.character(x)
  if (is.logical(x)) return(as.numeric(x))
  if (is.character(x)) {
    xl <- tolower(x)
    return(ifelse(xl %in% c("yes","y","support","supported","agree","true","1"), 1,
           ifelse(xl %in% c("no","n","oppose","opposed","disagree","false","0"), 0,
           suppressWarnings(as.numeric(x)))))
  }
  if (is.numeric(x)) {
    ux <- unique(x[!is.na(x)])
    if (treat_1to4_as_binary && length(ux) > 0 && all(ux %in% 1:4))
      return(ifelse(x %in% c(3,4), 1, ifelse(x %in% c(1,2), 0, NA_real_)))
    if (length(ux) > 0 && all(ux %in% c(0,1))) return(x)
    if (length(ux) > 0 && all(ux %in% c(1,2))) return(ifelse(x == 2, 1, 0))
    return(x)
  }
  suppressWarnings(as.numeric(x))
}
```

### Contact by Party (2-Group)

```{r contact-by-party-2group, fig.height=8}
# Prepare data with 2-group party classification
wide_df_party <- survey_24_25_with_party %>%
  mutate(
    row_id = row_number(),
    party_group = case_when(
      political_party %in% c(12503, 12504) ~ "Democrats",
      political_party %in% c(12505, 12506) ~ "Republicans",
      political_party == 12507 ~ "Independent/Other",
      political_party == 12618 ~ "No Party Affiliation",
      TRUE ~ NA_character_
    )
  ) %>%
  select(row_id, wave, wt, party_group, matches("_policy\\.contact$")) %>%
  filter(!is.na(party_group))

long_df_party <- wide_df_party %>%
  pivot_longer(
    cols = matches("_policy\\.contact$"),
    names_to = "behavior_var",
    names_pattern = "^(.+)_policy\\.contact$",
    values_to = "contact"
  ) %>%
  mutate(
    behavior_label = behaviors[behavior_var],
    contact01 = to01(contact, treat_1to4_as_binary = FALSE)
  ) %>%
  filter(!is.na(behavior_label), !is.na(contact01), !is.na(wt), !is.na(wave), !is.na(party_group))

# Calculate estimates
contact_est_party <- long_df_party %>%
  group_by(behavior_label, wave, party_group) %>%
  summarise(
    mean = weighted.mean(contact01, wt, na.rm = TRUE) * 100,
    n = n(),
    se = sqrt((mean/100) * (1 - mean/100) / n) * 100,
    conf.low = pmax(0, mean - 1.96 * se),
    conf.high = pmin(100, mean + 1.96 * se),
    .groups = "drop"
  )

# Create faceted plot
p <- ggplot(contact_est_party,
            aes(x = factor(wave), y = mean, group = party_group,
                color = party_group, shape = party_group)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2, alpha = 0.5) +
  geom_line(aes(linetype = party_group)) +
  geom_point(size = 2.5, alpha = 0.9) +
  facet_wrap(~ behavior_label, ncol = 2, scales = "free_y") +
  scale_color_manual(values = party_colors, name = "Political Party") +
  scale_linetype_manual(values = c("Democrats" = "solid", "Republicans" = "solid",
                                   "Independent/Other" = "dashed", "No Party Affiliation" = "dotted"),
                        name = "Political Party") +
  scale_shape_manual(values = c("Democrats" = 16, "Republicans" = 17,
                                "Independent/Other" = 15, "No Party Affiliation" = 18),
                     name = "Political Party") +
  scale_y_continuous(labels = function(x) paste0(x, "%"), limits = c(0, NA)) +
  labs(
    title = "Willingness to Contact Representatives by Political Party",
    subtitle = "% of U.S. adults willing to contact representatives by party affiliation",
    x = "", y = "",
    caption = "Source: Climate Culture Index, Rare, 2025"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    plot.title = element_text(face = "bold"),
    strip.text = element_text(face = "bold"),
    panel.spacing = unit(1, "lines")
  ) +
  guides(color = guide_legend(nrow = 1), linetype = guide_legend(nrow = 1), shape = guide_legend(nrow = 1))

ggplotly(p, tooltip = c("x", "y", "color")) %>%
  layout(legend = list(orientation = "h", y = -0.15))
```

### Policy Support by Party

```{r support-by-party, fig.height=8}
# Prepare support data
wide_df_support <- survey_24_25_with_party %>%
  mutate(
    row_id = row_number(),
    party_group = case_when(
      political_party %in% c(12503, 12504) ~ "Democrats",
      political_party %in% c(12505, 12506) ~ "Republicans",
      political_party == 12507 ~ "Independent/Other",
      political_party == 12618 ~ "No Party Affiliation",
      TRUE ~ NA_character_
    )
  ) %>%
  select(row_id, wave, wt, party_group, matches("_policy\\.support$")) %>%
  filter(!is.na(party_group))

long_df_support <- wide_df_support %>%
  pivot_longer(
    cols = matches("_policy\\.support$"),
    names_to = "behavior_var",
    names_pattern = "^(.+)_policy\\.support$",
    values_to = "support"
  ) %>%
  mutate(
    behavior_label = behaviors[behavior_var],
    support01 = to01(support, treat_1to4_as_binary = TRUE)
  ) %>%
  filter(!is.na(behavior_label), !is.na(support01), !is.na(wt), !is.na(wave), !is.na(party_group))

# Calculate estimates
support_est_party <- long_df_support %>%
  group_by(behavior_label, wave, party_group) %>%
  summarise(
    mean = weighted.mean(support01, wt, na.rm = TRUE) * 100,
    n = n(),
    se = sqrt((mean/100) * (1 - mean/100) / n) * 100,
    conf.low = pmax(0, mean - 1.96 * se),
    conf.high = pmin(100, mean + 1.96 * se),
    .groups = "drop"
  )

# Create faceted plot
p <- ggplot(support_est_party,
            aes(x = factor(wave), y = mean, group = party_group,
                color = party_group, shape = party_group)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2, alpha = 0.5) +
  geom_line(aes(linetype = party_group)) +
  geom_point(size = 2.5, alpha = 0.9) +
  facet_wrap(~ behavior_label, ncol = 2, scales = "free_y") +
  scale_color_manual(values = party_colors, name = "Political Party") +
  scale_linetype_manual(values = c("Democrats" = "solid", "Republicans" = "solid",
                                   "Independent/Other" = "dashed", "No Party Affiliation" = "dotted"),
                        name = "Political Party") +
  scale_shape_manual(values = c("Democrats" = 16, "Republicans" = 17,
                                "Independent/Other" = 15, "No Party Affiliation" = 18),
                     name = "Political Party") +
  scale_y_continuous(labels = function(x) paste0(x, "%"), limits = c(0, 100)) +
  labs(
    title = "Policy Support by Political Party",
    subtitle = "% of U.S. adults who support climate policies by party affiliation",
    x = "", y = "",
    caption = "Source: Climate Culture Index, Rare, 2025"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    plot.title = element_text(face = "bold"),
    strip.text = element_text(face = "bold"),
    panel.spacing = unit(1, "lines")
  ) +
  guides(color = guide_legend(nrow = 1), linetype = guide_legend(nrow = 1), shape = guide_legend(nrow = 1))

ggplotly(p, tooltip = c("x", "y", "color")) %>%
  layout(legend = list(orientation = "h", y = -0.15))
```

### Contact by Support Status

This analysis examines willingness to contact representatives among those who **support** vs. **do not support** each policy.

```{r contact-by-support-status, fig.height=10}
# Prepare data with support status
wide_df_combined <- survey_24_25_with_party %>%
  mutate(row_id = row_number()) %>%
  select(row_id, wave, wt, matches("_policy\\.(support|contact)$"))

long_df_combined <- wide_df_combined %>%
  pivot_longer(
    cols = matches("_policy\\.(support|contact)$"),
    names_to = c("behavior_var", "measure"),
    names_pattern = "^(.+)_policy\\.(support|contact)$",
    values_to = "value"
  ) %>%
  pivot_wider(names_from = measure, values_from = value) %>%
  mutate(
    behavior_label = behaviors[behavior_var],
    support01 = to01(support, treat_1to4_as_binary = TRUE),
    contact01 = to01(contact, treat_1to4_as_binary = FALSE),
    support_label = ifelse(support01 == 1, "Supporters", "Non-supporters")
  ) %>%
  filter(!is.na(behavior_label), !is.na(contact01), !is.na(support01), !is.na(wt), !is.na(wave))

# Calculate estimates
contact_by_support <- long_df_combined %>%
  group_by(behavior_label, wave, support_label) %>%
  summarise(
    mean = weighted.mean(contact01, wt, na.rm = TRUE) * 100,
    n = n(),
    se = sqrt((mean/100) * (1 - mean/100) / n) * 100,
    conf.low = pmax(0, mean - 1.96 * se),
    conf.high = pmin(100, mean + 1.96 * se),
    .groups = "drop"
  )

# Create faceted plot
support_colors <- c("Supporters" = "#008542", "Non-supporters" = "#AA1948")

p <- ggplot(contact_by_support,
            aes(x = factor(wave), y = mean, group = support_label,
                color = support_label, linetype = support_label)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.15, alpha = 0.6, linetype = "solid") +
  geom_line(linewidth = 1) +
  geom_point(size = 3, alpha = 0.95) +
  facet_wrap(~ behavior_label, ncol = 2) +
  scale_color_manual(values = support_colors, name = "Policy Support") +
  scale_linetype_manual(values = c("Supporters" = "solid", "Non-supporters" = "dashed"),
                        name = "Policy Support") +
  scale_y_continuous(labels = function(x) paste0(x, "%"), limits = c(0, 25)) +
  labs(
    title = "Willingness to Contact Representatives by Policy Support Status",
    subtitle = "Supporters are more likely to contact representatives about climate policies",
    x = "", y = "% Willing to Contact",
    caption = "Source: Climate Culture Index, Rare, 2025"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    plot.title = element_text(face = "bold"),
    strip.text = element_text(face = "bold"),
    panel.spacing = unit(1.2, "lines")
  )

ggplotly(p, tooltip = c("x", "y", "color")) %>%
  layout(legend = list(orientation = "h", y = -0.12))
```

---

<div class="footer-note">
<p><strong>Climate Culture Index 2025</strong> | Rare</p>
<p>For more information, visit <a href="https://rare.org/climate-culture-index/">rare.org/climate-culture-index</a></p>
</div>
